Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-02-13 Multiresolution_framework/ltx/manuscript.tex
minor edit to table one
minor edit to Table one
minor edit to teble one

\section{IDE Neural Field Model}
\singlespacing
\begin{table*}[!t]
\begin{tabular}{|l|l|l|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Units}\\
	\hline
	\multicolumn{3}{|c|}{\emph{Domain and indices}}\\
	\hline
	$\Omega$ & Spatial domain & n.a.\\
	$\mathbf{r}$ & Spatial location & [mm, mm]\\
	$t$ & Time & s\\
	\hline
	\multicolumn{3}{|c|}{\emph{Model}}\\
	\hline
    $y_t$ & Observation & mV\\
    $v(\mathbf{r},t)$ & Mean membrane potential & mV \\
	$f(v\left(\mathbf{r},t\right))$ & Firing rate function & spikes.s$^{-1}$\\
	$e_t(\mathbf{r})$ & Field disturbance, with covariance function $\eta(\mathbf r-\mathbf r')$ & mV\\
	$\boldsymbol\epsilon_t$ & Observation noise, with covariance matrix $\Sigma_\epsilon$ & mV\\
	$m(\mathbf{r}_n)$ & Observation kernel where $n$ is sensor index $n=1,..,n_y$ & n.a. \\
	$w(\mathbf{r})$ & Spatial connectivity kernel & n.a.\\
	$h(t)$ & Post-synaptic response kernel & mV\\
	$\tau$, $\xi$ & Membrane time constant \& time constant parameter & s, n.a.\\
	$\delta(t)$ & Dirac-delta function & n.a.\\
	\hline    
	\multicolumn{3}{|c|}{\emph{Multi-resolution Approximation}} \\
	\hline                                                   
	$\phi_{j,l}(r)$&Scaling function&n.a\\
	$\psi_{j,l}(r)$&Wavelet function&n.a\\  
	$\alpha_{j_0,l}, \beta_{j,l}$&Connectivity kernel approximation and detail coefficients&mV~spike$^{-1}$\\ 
	$x_{t,j_{0},l},\check{x}_{t,j,l}$&Field approximation and detail coefficients at a given time&mV~spike$^{-1}$\\ 
	$N_m(r)$&$m^{th}$ order B-spline function&n.a.\\
	$\varphi_m(r)$&$m^{th}$ order B-spline wavelet function&n.a.\\
	\hline
	\multicolumn{3}{|c|}{\emph{Reduced Model}} \\
	\hline
		$\boldsymbol\mu(r)$&Vector of $n_x$ field scaling and wavelet functions&n.a.\\
		$\boldsymbol\lambda(r)$&Vector of $n_{\boldsymbol\theta}$ connectivity kernel scaling and wavelet functions&n.a.\\
   	$\mathbf{x}_t$ & State vector at time $t$ composed of  $x_{t,j_{0},l}$ and $\check{x}_{t,j,l}$ & mV\\ 
		$\boldsymbol\theta$&Vector of connectivity kernel parameters composed of $\alpha_{j_0,l}$ and $\beta_{j,l}$& mV.spike$^{-1}$\\ 
		$\boldsymbol{\Lambda}_x$&Inner product of field basis functions&n.a.\\
		$\boldsymbol\Gamma, \boldsymbol\Lambda_{\boldsymbol{\theta}}$&Decomposition connectivity matrices&n.a.\\
   	$\mathbf{w}_t$ & State disturbance vector, with covariance $\Sigma_w$ & mV\\ 
    $\mathbf{A}(\boldsymbol{\theta})$& State transition matrix& n.a.\\
   	$\mathbf{C}$ & Observation matrix & n.a. \\
	\hline
	\multicolumn{3}{|c|}{\emph{Frequency Analysis}} \\
	\hline
	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cutoff frequency & cycles/mm \\
	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & (cycles/mm)$^2$\\
	\hline
	\multicolumn{3}{|c|}{\emph{Estimation}} \\
	\hline
	$\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^f$ & Forward prior and posterior state estimates & mV\\
	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior state estimates & mV\\
	$P^{f-}_t$, $P^f_t$  & Forward prior and posterior covariance matrices & mV$^2$\\
	$P^b_t$ & Backward posterior covariance matrices & mV$^2$\\
	$M_t$& Cross-covariance matrix & mV$^2$\\
	$\mathcal K_{t} $ & Filter gain & n.a.\\ 
	$\mathcal S_{t} $ & Smoother gain & n.a.\\ 
	$\boldsymbol\Xi_1, \boldsymbol\Xi_0$&Expected covariance and cross-covariance matrices& mV$^2$\\ 
	$\mathcal{Q}(\boldsymbol{\theta},\boldsymbol\theta')$&Lower bound on log-likelihood function&n.a.\\
	$\boldsymbol\nu_0$, $\boldsymbol\nu_1$&Lower bound coefficient matrices&n.a.\\ 
	$\boldsymbol\Upsilon$&Lower bound coefficient matrix&mV$^{-1}$.spike\\
	\hline
\end{tabular}
\caption{\textbf{Notation.} The first column of the table gives the symbols for all the notation used in the paper. The second column provides a brief description of the quantity, and the third column provides the SI units where relevant.}
\label{tab:Notation}
\end{table*}  
\doublespacing

>>>>

\section{IDE Neural Field Model}
\singlespacing
\begin{table*}[!t]
\begin{tabular}{|l|l|l|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Units}\\
	\hline
	\multicolumn{3}{|c|}{\emph{Domain and indices}}\\
	\hline
	$\Omega$ & Spatial domain & n.a.\\
	$\mathbf{r}$ & Spatial location & [mm, mm]\\
	$t$ & Time & s\\
	\hline
	\multicolumn{3}{|c|}{\emph{Model}}\\
	\hline
    $y_t$ & Observation & mV\\
    $v(\mathbf{r},t)$ & Mean membrane potential & mV \\
	$f(v\left(\mathbf{r},t\right))$ & Firing rate function & spikes.s$^{-1}$\\
	$e_t(\mathbf{r})$ & Field disturbance, with covariance function $\eta(\mathbf r-\mathbf r')$ & mV\\
	$\boldsymbol\epsilon_t$ & Observation noise, with covariance matrix $\Sigma_\epsilon$ & mV\\
	$m(\mathbf{r}_n)$ & Observation kernel where $n$ is sensor index $n=1,..,n_y$ & n.a. \\
	$w(\mathbf{r})$ & Spatial connectivity kernel & n.a.\\
	$h(t)$ & Post-synaptic response kernel & mV\\
	$\tau$, $\xi$ & Membrane time constant \& time constant parameter & s, n.a.\\
	$\delta(t)$ & Dirac-delta function & n.a.\\
	\hline    
	\multicolumn{3}{|c|}{\emph{Multi-resolution Approximation}} \\
	\hline                                                   
	$\phi_{j,l}(r)$&Scaling function&n.a\\
	$\psi_{j,l}(r)$&Wavelet function&n.a\\  
	$\alpha_{j_0,l}, \beta_{j,l}$&Connectivity kernel approximation and detail coefficients&mV~spike$^{-1}$\\ 
	$x_{t,j_{0},l},\check{x}_{t,j,l}$&Field approximation and detail coefficients at a given time&mV~spike$^{-1}$\\ 
	$N_m(r)$&$m^{th}$ order B-spline function&n.a.\\
	$\varphi_m(r)$&$m^{th}$ order B-spline wavelet function&n.a.\\
	\hline
	\multicolumn{3}{|c|}{\emph{State-Space Model}} \\
	\hline
		$\boldsymbol\mu(r)$&Vector of $n_x$ field scaling and wavelet functions&n.a.\\
		$\boldsymbol\lambda(r)$&Vector of $n_{\boldsymbol\theta}$ connectivity kernel scaling and wavelet functions&n.a.\\
   	$\mathbf{x}_t$ & State vector at time $t$ composed of  $x_{t,j_{0},l}$ and $\check{x}_{t,j,l}$ & mV\\ 
		$\boldsymbol\theta$&Vector of connectivity kernel parameters composed of $\alpha_{j_0,l}$ and $\beta_{j,l}$& mV.spike$^{-1}$\\ 
		$\boldsymbol{\Lambda}_x$&Inner product of field basis functions&n.a.\\
		$\boldsymbol\Gamma, \boldsymbol\Lambda_{\boldsymbol{\theta}}$&Decomposition connectivity matrices&n.a.\\
   	$\mathbf{w}_t$ & State disturbance vector, with covariance $\Sigma_w$ & mV\\ 
    $\mathbf{A}(\boldsymbol{\theta})$& State transition matrix& n.a.\\
   	$\mathbf{C}$ & Observation matrix & n.a. \\
	\hline
	\multicolumn{3}{|c|}{\emph{Frequency Analysis}} \\
	\hline
	$\boldsymbol{\nu}$& spatial frequency  & cycles/mm \\
	\hline
	\multicolumn{3}{|c|}{\emph{Estimation}} \\
	\hline
	$\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^f$ & Forward prior and posterior state estimates & mV\\
	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior state estimates & mV\\
	$\mathbf P^{f-}_t$, $\mathbf P^f_t$  & Forward prior and posterior covariance matrices & mV$^2$\\
	$\mathbf P^b_t$ & Backward posterior covariance matrices & mV$^2$\\
	$\mathbf M_t$& Cross-covariance matrix & mV$^2$\\
	$\mathcal K_{t} $ & Filter gain & n.a.\\ 
	$\mathcal S_{t} $ & Smoother gain & n.a.\\ 
	$\boldsymbol\Xi_1, \boldsymbol\Xi_0$&Expected covariance and cross-covariance matrices& mV$^2$\\ 
	$\mathcal{Q}(\boldsymbol{\theta},\boldsymbol\theta')$&Lower bound on log-likelihood function&n.a.\\
	$\boldsymbol\nu_0$, $\boldsymbol\nu_1$&Lower bound coefficient matrices&n.a.\\ 
	$\boldsymbol\Upsilon$&Lower bound coefficient matrix&mV$^{-1}$.spike\\
	\hline
\end{tabular}
\caption{\textbf{Notation.} The first column of the table gives the symbols for all the notation used in the paper. The second column provides a brief description of the quantity, and the third column provides the SI units where relevant.}
\label{tab:Notation}
\end{table*}  
\doublespacing
